GeckoGraph: A Visual Language for Polymorphic Types

### 2025-10-26 response.tex

\reply We now explicitly mark speculative interpretations in Section~6 (\textit{Discussion}) with leading phrases such as “We hypothesize that...”.

\pointRaised{Comment 7:}{Wording and grammar issues.}

\reply We have corrected numerous stylistic and grammatical errors, including:
“expressiveness power” → “expressiveness”,
“high-order function” → “higher-order function”,
and “GechoGraph” → “GeckoGraph.”  
Unclear terms such as “tangibly” and “regular higher-order function” have been clarified or replaced with precise expressions and supported with examples.  
We also removed unnecessary spaces before footnote labels.

\pointRaised{Comment 8:}{Clairify the syntactic sugar of curried function (Section 3)}

\reply We explicitly clarify that function notation \texttt{a -> b -> c } desugars to \texttt{a -> (b -> c) }, which has a consistent representation in GeckoGraph.

@@

\reply We clarified that participants report their programming experience once, before beginning the tasks.

\pointRaised{Comment 10:}{Distinguish between empirical findings and authors’ interpretations in the Discussion.}

\reply We now explicitly distinguish between observed results and speculative interpretations in the \textit{Discussion}, using clear phrases such as “We hypothesize that...” to signal interpretive commentary.

\pointRaised{Comment 11:}{Add reference for “between-subject design.”}

@@

\reply We now correctly cite Fisher, R.A. {\it The Design of Experiements} for the phase "between-subject design."

\pointRaised{Comment 12:}{Wording and grammar issues.}

\reply We have corrected numerous stylistic and grammatical errors, including:
Unclear terms such as “approximity” and “during type errors” have been clarified or replaced with precise expressions and supported with examples.

### 2025-10-26 main.tex
More changes

% In Section~\ref{sec:type-systems}, we review key type system features in functional programming languages, many of which have recently been adopted by object-oriented and multi-paradigm languages. We highlight how these features enable flexible abstraction and expressive type modeling, while sometimes hindering usability for beginners. Section~\ref{sec:gecko-graph} presents the design of GeckoGraph, illustrating how it visualizes complex type-level information that is often implicit or hard to interpret textually. Section~\ref{sec:evaluation} describes our user study, ZeroToHero, a series of 10 programming challenges, along with the study design, recruitment, and hypotheses. Section~\ref{sec:results} reports quantitative and qualitative findings, including completion time, success rates, and participant feedback. In Section~\ref{sec:discussion}, we interpret these results, discuss GeckoGraph’s benefits and usability challenges, and explore potential applications. Section~\ref{sec:related-work} reviews related visualization research, and Section~\ref{sec:conclusion} summarizes our contributions and outlines future directions.

@@

Curried functions (e.g., \texttt{ a -> b -> c}) are displayed as two cells of functions merged together \includegraphics[height=1em]{figures/Curry.png}. It appears as if the second function covers the right half of the first function, indicating that the second function is the return type of the first. Regular high-order functions (e.g., \texttt{(a -> b) -> c}) follow the rules of functions and nested data types \includegraphics[height=1.2em]{figures/HOF.png}. The placement of function indicators aims to make it easy to find desired functions in the documentation site based on function arity and higher-order functions (design goal \ref{goal3}). It is easy to tell high-order functions from the vertical position of the function indicators. Similarly, it is easy to count the arity of a function by counting the number of function indicators at the outer layer. For example, in Fig. \ref{fig:indicator}, the outer layer function indicators (the ones colored in the lightest shade of gray) suggest a ternary function. The two argument types and the return type are all functions.

@@

\begin{figure}[ht]
  \includegraphics[width=\linewidth]{figures/SuccessfulRate}
  \caption{\label{fig:success-rate}{\bf Success rate of each task, with 95\% confidence interval, grouped by experience level.} The figure is cropped from 50\% to 100\% for readability. Bootstrapping was used for computing the confidence interval because of the non-normal distribution. In most tasks, GeckoGraph provides a small edge. However, significant differences were found in task 10 of the beginner group and task 10 of the familiar group. }
\end{figure}

>>>>

In Section~\ref{sec:type-systems}, we review key type system features in functional programming languages, many of which have recently been adopted by object-oriented and multi-paradigm languages. We highlight how these features enable flexible abstraction and expressive type modeling, while sometimes hindering usability for beginners. Section~\ref{sec:gecko-graph} presents the design of GeckoGraph, illustrating how it supports the type level features outlined in Section~\ref{sec:type-systems}. Section~\ref{sec:evaluation} describes our user study, ZeroToHero, a series of 10 programming challenges, along with the study design, recruitment, and hypotheses. Section~\ref{sec:results} reports quantitative and qualitative findings, including completion time, success rates, and participant feedback. In Section~\ref{sec:discussion}, we interpret these results, discuss GeckoGraph’s benefits and usability challenges, and explore potential applications. Section~\ref{sec:related-work} reviews related visualization research, and Section~\ref{sec:conclusion} summarizes our contributions and outlines future directions.

@@

Curried functions are functions that return other functions (e.g. \texttt{ a -> (b -> c)}). In functional languages, they are often written with a syntactic shorthand, such as \texttt{ a -> b -> c}). These two forms are uniquely represented in GeckoGraph as two functions cells merged together \includegraphics[height=1em]{figures/Curry.png}. It appears as if the second function covers the right half of the first function, indicating that the second function is the return type of the first. Regular high-order functions (e.g., \texttt{(a -> b) -> c}) follow the rules of functions and nested data types \includegraphics[height=1.2em]{figures/HOF.png}. The placement of function indicators aims to make it easy to find desired functions in the documentation site based on function arity and higher-order functions (design goal \ref{goal3}). It is easy to tell high-order functions from the vertical position of the function indicators. Similarly, it is easy to count the arity of a function by counting the number of function indicators at the outer layer. For example, in Fig. \ref{fig:indicator}, the outer layer function indicators (the ones colored in the lightest shade of gray) suggest a ternary function. The two argument types and the return type are all functions.

@@

\begin{figure}[ht]
  \includegraphics[width=\linewidth]{figures/SuccessfulRate}
  \caption{\label{fig:success-rate}{\bf Success rate of each task, with 95\% confidence interval, grouped by experience level.} The figure is cropped from 50\% to 100\% for readability. Bootstrapping was used for computing the confidence interval because of the non-normal distribution. In most tasks, GeckoGraph provides no significant differences. However, substantial improvements were observed in task 10 for the beginner group (14.5\%) and the familiar group (11.2\%). }
\end{figure}
